On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-09 Manuscript/manuscript.tex
replied to minor comments

Block bootstrap is a tool to construct confidence intervals (CI) to make
inferences about dependent data. Essentially, it depends on correct estimation
of the uncertainty in the estimation, similar to the standard bootstrap 
\citep{efron1979bootstrap}, but for serially dependent data.
Early ideas of block bootstrap were developed not long after the standard 
bootstrap.\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife} It 
has since
been applied in various fields, for instance, econometrics and 
meteorology.\citep{mackinnon2006bootstrap, varga2017generalised}
Block bootstrap is especially useful for serially dependent data when the serial 
dependence is not specified or not of primary interest. The method is expected 
to produce CIs with coverage rates matching their nominal levels as the sample 
size grows. However, when dealing with finite sample sizes, an important 
question is how large the sample size must be for block bootstrap CIs to have 
the desired coverage rates.

@@

Block bootstrap is a useful method for estimating parameters of a time series,
from simple parameters like the mean to more complicated temporal dependence
factors. We know theoretically that the block bootstrap procedure will cover a 
parameter of a time series at the nominal level given an infinitely large
\jy{Also cite Calhoun in the introduction}
sample,\citep{calhoun2018} so the goal for this study was to find the smallest 
finite sample length~$n$
of a time series in order for the block bootstrap procedure to recover its 
associated parameters at an acceptable rate. Our analysis relies on the 
assumption that there is a size $n$ large enough for the method to work: that 
is, the method's performance improves as $n$ increases. Out of the six types of 
intervals used in this study, this assumption was found to hold true with 
respect to estimating $\phi$ only for standard normal, Student's $t$, and recentered 
percentile CIs, whereas percentile, BC, and BCA intervals exhibited coverage 
deterioration as $n$ increased. The percentile CI's coverage deterioration can 
be attributed to bias that is not corrected as $n$ increases. Specifically, as 
$n$ increases, the width of the CI decreases, but because the percentile CI 
underestimates $\phi$, the coverage decreases. The BC CI seems to correct the 
bias, but the width of the CI seems to be too short. The acceleration factor 
of the BCA CI seems to fail, as the width of the CI seems to be too
short.

@@

Based on \textbf{Figure~\ref{fig:norm2}}, for negative autocorrelations, the 
coverage 
rates of $\mu$ appear to be lower when
using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
for smaller values of~$n$. The results for $\sigma_x$ with $l = \lceil 2n^{1/3} 
\rceil$ look very similar to 
those the results for $\sigma_x$ with $l = \lceil n^{1/3} \rceil$, but coverage 
rates of $\sigma_x$ do look slightly lower
especially for negative values of $\phi$, although Student's $t$ CIs are again
not as influenced by this change in~$l$. A larger sample size seems necessary
when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.
\jy{Put the small paragraphs into a bigger one.}\mc{addressed}
Recentered percentile and standard CIs have slightly lower coverage rates when
estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
Although it is still a problem, the coverage deterioration appears to be less 
dramatic for BCA,
BC, and percentile CIs. Aside from these differences, the overall changes
in performance when other experimental factors are changed are the same as
when $l = \lceil n^{1/3} \rceil$.

>>>>

Block bootstrap is a tool to construct confidence intervals (CI) to make
inferences about dependent data. Essentially, it depends on correct estimation
of the uncertainty in the estimation, similar to the standard bootstrap 
\citep{efron1979bootstrap}, but for serially dependent data.
Early ideas of block bootstrap were developed not long after the standard 
bootstrap.\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife} It 
has since
been applied in various fields, for instance, econometrics and 
meteorology.\citep{mackinnon2006bootstrap, varga2017generalised}
Block bootstrap is especially useful for serially dependent data when the serial 
dependence is not specified or not of primary interest. The method is expected 
to produce CIs with coverage rates matching their nominal levels as the sample 
size grows.\citep{calhoun2018} However, when dealing with finite sample sizes, 
an important 
question is how large the sample size must be for block bootstrap CIs to have 
the desired coverage rates.

@@

Block bootstrap is a useful method for estimating parameters of a time series,
from simple parameters like the mean to more complicated temporal dependence
factors. We know theoretically that the block bootstrap procedure will cover a 
parameter of a time series at the nominal level given an infinitely large
%\jy{Also cite Calhoun in the introduction}\mc{addressed}
sample,\citep{calhoun2018} so the goal for this study was to find the smallest 
finite sample length~$n$
of a time series in order for the block bootstrap procedure to recover its 
associated parameters at an acceptable rate. Our analysis relies on the 
assumption that there is a size $n$ large enough for the method to work: that 
is, the method's performance improves as $n$ increases. Out of the six types of 
intervals used in this study, this assumption was found to hold true with 
respect to estimating $\phi$ only for standard normal, Student's $t$, and recentered 
percentile CIs, whereas percentile, BC, and BCA intervals exhibited coverage 
deterioration as $n$ increased. The percentile CI's coverage deterioration can 
be attributed to bias that is not corrected as $n$ increases. Specifically, as 
$n$ increases, the width of the CI decreases, but because the percentile CI 
underestimates $\phi$, the coverage decreases. The BC CI seems to correct the 
bias, but the width of the CI seems to be too short. The acceleration factor 
of the BCA CI seems to fail, as the width of the CI seems to be too
short.

@@

Based on \textbf{Figure~\ref{fig:norm2}}, for negative autocorrelations, the 
coverage 
rates of $\mu$ appear to be lower when
using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
for smaller values of~$n$. The results for $\sigma_x$ with $l = \lceil 2n^{1/3} 
\rceil$ look very similar to 
those the results for $\sigma_x$ with $l = \lceil n^{1/3} \rceil$, but coverage 
rates of $\sigma_x$ do look slightly lower
especially for negative values of $\phi$, although Student's $t$ CIs are again
not as influenced by this change in~$l$. A larger sample size seems necessary
when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.
%\jy{Put the small paragraphs into a bigger one.}\mc{addressed}
Recentered percentile and standard CIs have slightly lower coverage rates when
estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
Although it is still a problem, the coverage deterioration appears to be less 
dramatic for BCA,
BC, and percentile CIs. Aside from these differences, the overall changes
in performance when other experimental factors are changed are the same as
when $l = \lceil n^{1/3} \rceil$.
